Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-02 paper/ms.tex
Fix paper temporarily
Add Rn plot to paper
Add some text to describe Rn plot

We use the relation in Figure~\ref{fig:range_deltaphi}, which shows the
typical $z$ offset at each $\Delta \phi$, to convert a given $z$ offset into a
$\Delta\phi$, which we then convert into a chord length which we interpret as
$R_{\n}$. The result of this procedure is shown in Figure~\ref{fig:Rn_mc}.

\begin{figure*}
\plotone{fig/}
\end{figure*}

>>>>

We use the relation in Figure~\ref{fig:range_deltaphi}, which shows the
typical $z$ offset at each $\Delta \phi$, to convert a given $z$ offset into a
$\Delta\phi$, which we then convert into a chord length which we interpret as
$R_{\n}$, the neighborhood around the cluster. If the $z$~offset is greater
than the maximum range value of the galaxy, we simply report the maximum chord
length ($2\times8.2\,\kpc$). The result of this procedure is shown in
Figure~\ref{fig:Rn_mc}. The solid lines indicate the neighborhood values
assuming the mean relation between $z$~offset and $m_c$, and the dashed lines
show the $+1\,\sigma$ and $-1\,\sigma$ relations, indicative of the strong
$\phi$-dependence of the midplane effect.

Figure~\ref{fig:Rn_mc} is most informative for the low $J_z$ orbit (blue). The
neighborhood around $\sim100\Msun$ clusters can be as small as $\sim300\,\pc$
but up to $\sim1.2\,\kpc$ for m12i and m12f, though the situation is
marginally better for m12m with values ranging from $\sim0.8\,\kpc$ to
$\sim3\,\kpc$. The neighborhood values steadily increase with $m_c$, topping
out at $\sim5\,\kpc$ for $\sim10^4\,\Msun$ clusters in m12i and m12f. In m12m,
the neighborhood value reaches the maximum allowed of $16.4\,\kpc$ for
clusters of mass $\sim800\,\Msun$. The interpretation of this is that the
expected action space dispersion is so high for such high mass clusters that
the measured $z$~offset is not large enough throughout the entire galaxy to be
important.

For the medium $J_z$ orbit (orange), the situation is better, although such an
orbit is not a good fit to any of the nearby open clusters \Gus{Table x}. For
m12i and m12f, the neighborhood is $\sim \text{few}\,\kpc$ for
$m_c\sim10^2\,\Msun$. At $\sim10^3\,\Msun$ the curves reach their maximum
value. For m12m, the neighborhood starts at $\sim10\,\kpc$ and quickly rises
to the maximum value. For the high $J_z$ orbit (red), the neighborhood is at
the maximum value for nearly all masses, except at the very low-mass end in
m12i.

\begin{figure*}
\plotone{fig/Rn_vs_mc.pdf}
\caption{Caption.}
\label{fig:Rn_mc}
\end{figure*}
